---
title: "HTS ML Analysis"
author: "Margie"
date: "4/3/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE
)
library(kableExtra)
library(formattable)
library(plotly)

```

```{r loaddata, include=FALSE, warning=FALSE,message=FALSE}
source("C:/Users/Admin/OneDrive/Analytics/HTS ML Output/HTS ML App County Predictions.R")
```

### HTS ML VALIDATION
This document shows validation summaries for the HTS Machine Learning Screening Application developed for `r unique(combi$county)` counties.

### Overall Positivity

```{r overallpositivity, echo=FALSE, 	fig.height = 10,	fig.width = 15}
ggplot(posit,aes(x=reorder(county, -positivity),y=positivity))+
  geom_bar(stat="identity",fill="steelblue")+
  geom_text(aes(label=paste0(round((positivity*100),digits=1),'%')), position=position_stack(vjust=1.05)) +
  ggtitle('Overall Positivity by County')+
  xlab('County')+ylab('Positivity') +
theme(
plot.title = element_text(color="#993333", size=16, face="bold.italic", hjust = 0.5),
axis.title.x = element_text(color="#993333", size=12),
axis.title.y = element_text(color="#993333", size=12)
)+
scale_y_continuous(labels = scales::percent,limit=c(0,0.06))

```
```{r overallpositivity_tbl, echo=FALSE}
tbl_combi<-posit %>% arrange(desc(positivity)) %>%
  mutate(positivity=paste0(round(positivity*100,digits = 1),'%')) 

tbl_combi %>% 
  kbl(caption ="<center><strong>Overall Positivity by County</strong></center>") %>%
  kable_classic_2(position = "center",html_font = "Arial Narrow",bootstrap_options = c("condensed","stripped"),full_width = T, font_size = 20)
```


### Positive Precision for Different by % of patients tested

```{r fig.height=5, fig.width=10}
combi_cum$groupRowGroup <- factor(combi_cum$RowGroup,      # Reordering group factor levels
                         levels = c("10", "20", "30", "40","50","60","70","80","90","100"))

ggplot(combi_cum,aes(x=-csum_pos_prec))+
  geom_line(aes(y=csum_pos_prec,group=1),position = 'dodge',color='red',size = 1)+
  geom_point(aes(y=csum_pos_prec,group=1))+
  geom_line(aes(y=csum_pos_rec,group=1),position = 'dodge',color='blue',size = 1)+
  geom_point(aes(y=csum_pos_rec,group=1))+
  ggtitle('Positivity by Risk Outcomes')+
  xlab('Risk Outcomes')+ylab('Positivity') +
theme(
plot.title = element_text(color="#993333", size=16, face="bold.italic", hjust = 0.5),
axis.title.x = element_text(color="#993333", size=12),
axis.title.y = element_text(color="#993333", size=12),
axis.text.x = element_text(size=10,angle=90,vjust=0.2)
)+
scale_y_continuous(labels = scales::percent)
```

Predictions are not binary "positive" or "negative"; rather, they are numbers between 0 to 1 akin to probabilities. For each threshold from 0 to 1, we calculate precision and recall and plot the points on a curve and thus come up with cut off points.

In HTS Model, there are 4 Risk Outcomes; `r unique(combi$RiskOutcome)`. Different cut-off marks are defined for the risk outcomes by different counties. Across models - the threshold is set based on precision, which is different for every county.

For Siaya County: we expect that of the people we test with a "Highest Risk Outcome" 75.2% will be positive

```{r precision, echo=FALSE}
combiHighRisk$groupCounty <- factor(combiHighRisk$county,      # Reordering group factor levels
                         levels = c("Siaya", "Homabay", "Nairobi", "Machakos"))

lbl=paste("n:",combiHighRisk$RowTots,"\n",paste0(round((combiHighRisk$prec_pos*100),digits=1),'%'))
pt_values <- combiHighRisk %>% select(RiskOutcome,county,rec_pos,prec_pos) %>% 
    group_by(RiskOutcome,county) 

ggplot(combiHighRisk)+
  geom_col(aes(x=reorder(RiskOutcome,-prec_pos),y=prec_pos,fill=RiskOutcome),stat="identity",position = 'dodge' )+
  geom_line(aes(x=reorder(RiskOutcome,-prec_pos), y=rec_pos,group=1),position = 'dodge',color='black',size = 0.5)+
  geom_point(aes(x=reorder(RiskOutcome,rec_pos), y=rec_pos),alpha = 0.5) +
  facet_wrap(. ~groupCounty)  +
  geom_text(aes(x=reorder(RiskOutcome,-prec_pos), y=prec_pos,label=lbl),vjust = 0.7,position = position_dodge(.9), size = 3.5, check_overlap = TRUE) +
  ggtitle('Positivity by Risk Outcomes')+
  xlab('Risk Outcomes')+ylab('Positivity') +
theme(
plot.title = element_text(color="#993333", size=16, face="bold.italic", hjust = 0.5),
axis.title.x = element_text(color="#993333", size=12),
axis.title.y = element_text(color="#993333", size=12),
axis.text.x = element_text(size=10,angle=90,vjust=0.2)
)+
scale_y_continuous(labels = scales::percent)


```


```{r echo=FALSE}
#Formatted Table 
tbl_combiRsk<-combiHighRisk %>% select(RiskOutcome,county,Negative,Positive,RowTots,prec_pos,Tot_Pos,rec_pos) %>%
  mutate(prec_pos=paste0(round(prec_pos*100,digits = 1),'%'),
         rec_pos=paste0(round(rec_pos*100,digits = 1),'%')
         ) %>% 
  rename(County=county,
        TotalTested=RowTots,
         Positivity=prec_pos,
         Recall=rec_pos,
         TotalPositive_col=Tot_Pos) %>%
  arrange(RiskOutcome,desc(Positivity))
tbl_combiRsk %>% kbl(caption ="<center><strong>Positivity by Risk Outcomes</strong></center>") %>%
  kable_classic("hover", full_width = F,html_font = "Cambria") 
```

```{r positivityAge, echo=FALSE, warning=FALSE}
# Output Positivity for Each County
posit_age <- combi %>% group_by(county,AgeGroup,FinalTestResult) %>% summarise(num=n()) %>% ungroup()
# Pivot Wider Final Test Result becomes the Columns, Risk Outcome becomes the Rows
posit_age <- posit_age %>% pivot_wider(names_from = FinalTestResult, values_from = num)
posit_age <-posit_age %>% mutate(TotalTested=Positive+Negative,
positivity=(Positive/TotalTested))

posit_age$county <- factor(posit_age$county,      # Reordering group factor levels
                         levels = c("Siaya", "Homabay", "Nairobi", "Machakos"))


ggplot(posit_age,aes(x=reorder(AgeGroup, -positivity),y=positivity,fill=AgeGroup))+
  geom_bar(stat="identity",position = 'dodge')+
  facet_grid(. ~county)  +
 geom_text(aes(label=paste0(round((positivity*100),digits=1),'%')),vjust = 1.09,
             position = position_dodge(.9), size = 4) +
  ggtitle('Positivity by Age Group')+
  xlab('Age Group')+ylab('Positivity') +
theme(
plot.title = element_text(color="#993333", size=16, face="bold.italic", hjust = 0.5),
plot.subtitle = element_text(hjust=0.5),
axis.title.x = element_text(color="#993333", size=12),
axis.title.y = element_text(color="#993333", size=12),
axis.text.x = element_text(size=10,angle=90,vjust=0.2)
)+
scale_y_continuous(labels = scales::percent)
```
```{r positivityAge_tbl, echo=FALSE}
posit_age %>% arrange(county,desc(AgeGroup)) %>%
  mutate(positivity=paste0(round(positivity*100,digits = 1),'%')) %>%
kbl(caption ="<center><strong>Positivity - Testing by Age Group</strong></center>") %>%
  kable_classic("hover", full_width = F,html_font = "Cambria") 
```


```{r precisionAge, echo=FALSE}
combiHighRisksAge$groupCounty <- factor(combiHighRisksAge$county,      # Reordering group factor levels
                         levels = c("Siaya", "Homabay", "Nairobi", "Machakos"))

ggplot(combiHighRisksAge,aes(x=reorder(RiskOutcome, -prec_pos),y=prec_pos,fill=AgeGroup))+
  geom_bar(stat="identity",position = 'dodge')+
  facet_grid(. ~groupCounty)  +
 geom_text(aes(label=paste0(round((prec_pos*100),digits=1),'%')),vjust = 1.09,
             position = position_dodge(.9), size = 3.5) +
  ggtitle('Positivity by Age Group - Different Risk Outcomes',subtitle ='When Different risks are tested')+
  xlab('Age Group')+ylab('Positivity') +
theme(
plot.title = element_text(color="#993333", size=16, face="bold.italic", hjust = 0.5),
plot.subtitle = element_text(hjust=0.5),
axis.title.x = element_text(color="#993333", size=12),
axis.title.y = element_text(color="#993333", size=12),
axis.text.x = element_text(size=10,angle=90,vjust=0.2)
)+
scale_y_continuous(labels = scales::percent)

```
```{r precisionAgeCty, echo=FALSE}

tbl_combiRskAge<-combiHighRisksAge %>% select(RiskOutcome,AgeGroup,county,Negative,Positive,RowTots,prec_pos,Tot_Pos,rec_pos) %>%
  mutate(prec_pos=paste0(round(prec_pos*100,digits = 1),'%'),
         rec_pos=paste0(round(rec_pos*100,digits = 1),'%')
         ) %>% 
  rename(County=county,
        TotalTested=RowTots,
         Positivity=prec_pos,
         Recall=rec_pos,
         TotalPositive_col=Tot_Pos) %>%
  arrange(RiskOutcome)
tbl_combiRskAge %>% kbl(caption ="<center><strong>Positivity - When Different Groups are Tested</strong></center>") %>%
  kable_classic_2("hover", full_width = T,html_font = "Cambria")
```



```{r}

```


